The problem and promise of scale in multilayer networks

### 2020-01-28 paper/manuscript.Rmd
interpret strength, neighbors

### Each metric's interpretation
* Multidegree: sum of degree across layers. High multidegree = connected to many individuals across layers. Low multidegree = not connected to many individuals across layers. 
* Degree deviation: deviation of degree across layers. High degree deviation = large difference between degree for an individual across layers. Low degree deviation = individuals are similarly connected across layers. 
*

>>>>

### Each metric's interpretation
* Multidegree: sum of degree across layers. High multidegree = connected to many individuals across layers. Low multidegree = not connected to many individuals across layers. 
* Degree deviation: deviation of degree across layers. High degree deviation = large difference between degree for an individual across layers. Low degree deviation = individuals are similarly connected across layers. 
* Graph strength: weighted version of degree. High graph strength = highly connected. Not summed in this case across layers. 
* Neighbors: number of unique individuals adjacent to each actor. Considered in a single layer, this is equal to the degree. 
* Neighborhood: number of unique individuals across all layers. High neighborhood = a high number of unique individuals connected to an actor. 
* Relevance: layer centric metric, corresponding to the number of neighbors on a layer divided by the total neighborhood for each actor. High relevance means that the layer is highly relevant to the individuals connections. A low relevance means this layer does not contribute many neighbors to an individuals overall neighborhood. 
* Connective redundancy: the total multilayer neighborhood divided by the multidegree. High connective redundancy indicates a multilayer network that has many repeated edges across layers between an actor and its neighbours. Low connective redundancy is
